The title

### 2023-04-13 doc/multiverse_skeleton.Rmd
Move to static branching (#87)
* make_model_list takes pa and sleep vars as args

* Fix number of imputations

Fixes #86

* Add log_pa_volume variable

* Clear up linting message in data_imp

* Manage control vars dynamically

* Use static branching

* Add vars attribute to model_list

Co-authored-by: James Conigrave <12742211+conig@users.noreply.github.com>

* Add pipeline tweaks to allow for log variable

Co-authored-by: James Conigrave <12742211+conig@users.noreply.github.com>

* Rerun pipeline

* rename weekday_x

* Automate docs

Co-authored-by: James Conigrave <12742211+conig@users.norep

In the following section we present models for a range of moderators which were pre-defined in our protocol.
\clearpage

## BMI

```{r}
tar_load(model_tables_by_bmi)
tar_load(purdy_pictures_by_bmi)
```

### The effects of physical activity volume on sleep by BMI

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
We estimated the effect of physical activity volume on sleep by BMI, and the results are presented in Table \@ref(tab:sleep-outcomes-by-bmi) and Figure \@ref(fig:sleep-by-volume-fig-by-bmi)

```{r sleep-outcomes-by-bmi}
papaja::apa_table(
  model_tables_by_bmi$sleep$data,
  caption = model_tables_by_bmi$sleep$caption,
  note = model_tables_by_bmi$sleep$note,
  col_spanners = model_tables_by_bmi$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig-by-bmi, fig.cap = "Sleep metrics on Physical activity volume by BMI"}
knitr::include_graphics(here::here(purdy_pictures_by_bmi$predictor_pa_volume), error = FALSE)
```

### The effects of physical activity intensity on sleep by BMI

We estimated how physical activity intensity affects sleep across BMI.
We present the results in Table \@ref(tab:sleep-outcomes-by-bmi) and Figure \@ref(fig:sleep-by-intensity-fig-by-bmi).

```{r sleep-by-intensity-fig-by-bmi, fig.cap = "Sleep metrics on Physical activity intensity moderated by BMI"}
knitr::include_graphics(here::here(purdy_pictures_by_bmi$predictor_pa_intensity), error = FALSE)
```

We estimated the effect of sleep duration on physical activity by BMI.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-bmi) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-bmi).

```{r pa-outcomes-by-bmi}
papaja::apa_table(
  model_tables_by_bmi$physical_activity$data,
  caption = model_tables_by_bmi$physical_activity$caption,
  note = model_tables_by_bmi$physical_activity$note,
  col_spanners = model_tables_by_bmi$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig-by-bmi, fig.cap = "Physical activity by sleep duration moderated by BMI"}
knitr::include_graphics(here::here(purdy_pictures_by_bmi$predictor_sleep_duration_lag), error = FALSE)
```

We estimated the effect of sleep efficiency on physical activity by BMI.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-bmi) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-bmi).

```{r PA-by-sleep-efficiency-fig-by-bmi, fig.cap = "Physical activity by sleep efficiency moderated by BMI"}
knitr::include_graphics(here::here(purdy_pictures_by_bmi$predictor_sleep_efficiency_lag), error = FALSE)
```

We estimated the effect of sleep onset on physical activity by BMI.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-bmi) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-bmi).

```{r PA-by-sleep-onset-fig-by-bmi, fig.cap = "Physical activity by sleep onset moderated by BMI"}
knitr::include_graphics(here::here(purdy_pictures_by_bmi$predictor_sleep_onset_lag), error = FALSE)
```

We estimated the effect of sleep regularity on physical activity by BMI.
Results are presented in Table \@ref(tab:pa-outcomes-by-bmi) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-bmi).

```{r PA-by-sleep-regularity-fig-by-bmi, fig.cap = "Physical activity by sleep regularity moderated by BMI"}
knitr::include_graphics(here::here(purdy_pictures_by_bmi$predictor_sleep_regularity_lag), error = FALSE)
```
\clearpage

## SES

```{r}
tar_load(model_tables_by_ses)
tar_load(purdy_pictures_by_ses)
```

### The effects of physical activity volume on sleep by SES

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
We estimated the effect of physical activity volume on sleep by SES, and the results are presented in Table \@ref(tab:sleep-outcomes-by-ses) and Figure \@ref(fig:sleep-by-volume-fig-by-ses)

```{r sleep-outcomes-by-ses}
papaja::apa_table(
  model_tables_by_ses$sleep$data,
  caption = model_tables_by_ses$sleep$caption,
  note = model_tables_by_ses$sleep$note,
  col_spanners = model_tables_by_ses$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig-by-ses, fig.cap = "Sleep metrics on Physical activity volume by SES"}
knitr::include_graphics(here::here(purdy_pictures_by_ses$predictor_pa_volume), error = FALSE)
```

### The effects of physical activity intensity on sleep by SES

We estimated how physical activity intensity affects sleep across SES.
We present the results in Table \@ref(tab:sleep-outcomes-by-ses) and Figure \@ref(fig:sleep-by-intensity-fig-by-ses).

```{r sleep-by-intensity-fig-by-ses, fig.cap = "Sleep metrics on Physical activity intensity moderated by SES"}
knitr::include_graphics(here::here(purdy_pictures_by_ses$predictor_pa_intensity), error = FALSE)
```

We estimated the effect of sleep duration on physical activity by SES.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-ses) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-ses).

```{r pa-outcomes-by-ses}
papaja::apa_table(
  model_tables_by_ses$physical_activity$data,
  caption = model_tables_by_ses$physical_activity$caption,
  note = model_tables_by_ses$physical_activity$note,
  col_spanners = model_tables_by_ses$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig-by-ses, fig.cap = "Physical activity by sleep duration moderated by SES"}
knitr::include_graphics(here::here(purdy_pictures_by_ses$predictor_sleep_duration_lag), error = FALSE)
```

We estimated the effect of sleep efficiency on physical activity by SES.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-ses) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-ses).

```{r PA-by-sleep-efficiency-fig-by-ses, fig.cap = "Physical activity by sleep efficiency moderated by SES"}
knitr::include_graphics(here::here(purdy_pictures_by_ses$predictor_sleep_efficiency_lag), error = FALSE)
```

We estimated the effect of sleep onset on physical activity by SES.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-ses) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-ses).

```{r PA-by-sleep-onset-fig-by-ses, fig.cap = "Physical activity by sleep onset moderated by SES"}
knitr::include_graphics(here::here(purdy_pictures_by_ses$predictor_sleep_onset_lag), error = FALSE)
```

We estimated the effect of sleep regularity on physical activity by SES.
Results are presented in Table \@ref(tab:pa-outcomes-by-ses) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-ses).

```{r PA-by-sleep-regularity-fig-by-ses, fig.cap = "Physical activity by sleep regularity moderated by SES"}
knitr::include_graphics(here::here(purdy_pictures_by_ses$predictor_sleep_regularity_lag), error = FALSE)
```
\clearpage

## sex

```{r}
tar_load(model_tables_by_sex)
tar_load(purdy_pictures_by_sex)
```

### The effects of physical activity volume on sleep by sex

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
We estimated the effect of physical activity volume on sleep by sex, and the results are presented in Table \@ref(tab:sleep-outcomes-by-sex) and Figure \@ref(fig:sleep-by-volume-fig-by-sex)

```{r sleep-outcomes-by-sex}
papaja::apa_table(
  model_tables_by_sex$sleep$data,
  caption = model_tables_by_sex$sleep$caption,
  note = model_tables_by_sex$sleep$note,
  col_spanners = model_tables_by_sex$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig-by-sex, fig.cap = "Sleep metrics on Physical activity volume by sex"}
knitr::include_graphics(here::here(purdy_pictures_by_sex$predictor_pa_volume), error = FALSE)
```

### The effects of physical activity intensity on sleep by sex

We estimated how physical activity intensity affects sleep across sex.
We present the results in Table \@ref(tab:sleep-outcomes-by-sex) and Figure \@ref(fig:sleep-by-intensity-fig-by-sex).

```{r sleep-by-intensity-fig-by-sex, fig.cap = "Sleep metrics on Physical activity intensity moderated by sex"}
knitr::include_graphics(here::here(purdy_pictures_by_sex$predictor_pa_intensity), error = FALSE)
```

We estimated the effect of sleep duration on physical activity by sex.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-sex) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-sex).

```{r pa-outcomes-by-sex}
papaja::apa_table(
  model_tables_by_sex$physical_activity$data,
  caption = model_tables_by_sex$physical_activity$caption,
  note = model_tables_by_sex$physical_activity$note,
  col_spanners = model_tables_by_sex$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig-by-sex, fig.cap = "Physical activity by sleep duration moderated by sex"}
knitr::include_graphics(here::here(purdy_pictures_by_sex$predictor_sleep_duration_lag), error = FALSE)
```

We estimated the effect of sleep efficiency on physical activity by sex.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-sex) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-sex).

```{r PA-by-sleep-efficiency-fig-by-sex, fig.cap = "Physical activity by sleep efficiency moderated by sex"}
knitr::include_graphics(here::here(purdy_pictures_by_sex$predictor_sleep_efficiency_lag), error = FALSE)
```

We estimated the effect of sleep onset on physical activity by sex.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-sex) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-sex).

```{r PA-by-sleep-onset-fig-by-sex, fig.cap = "Physical activity by sleep onset moderated by sex"}
knitr::include_graphics(here::here(purdy_pictures_by_sex$predictor_sleep_onset_lag), error = FALSE)
```

We estimated the effect of sleep regularity on physical activity by sex.
Results are presented in Table \@ref(tab:pa-outcomes-by-sex) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-sex).

```{r PA-by-sleep-regularity-fig-by-sex, fig.cap = "Physical activity by sleep regularity moderated by sex"}
knitr::include_graphics(here::here(purdy_pictures_by_sex$predictor_sleep_regularity_lag), error = FALSE)
```
\clearpage

## weekday

```{r}
tar_load(model_tables_by_weekday)
tar_load(purdy_pictures_by_weekday)
```

### The effects of physical activity volume on sleep by weekday

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
We estimated the effect of physical activity volume on sleep by weekday, and the results are presented in Table \@ref(tab:sleep-outcomes-by-weekday) and Figure \@ref(fig:sleep-by-volume-fig-by-weekday)

```{r sleep-outcomes-by-weekday}
papaja::apa_table(
  model_tables_by_weekday$sleep$data,
  caption = model_tables_by_weekday$sleep$caption,
  note = model_tables_by_weekday$sleep$note,
  col_spanners = model_tables_by_weekday$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig-by-weekday, fig.cap = "Sleep metrics on Physical activity volume by weekday"}
knitr::include_graphics(here::here(purdy_pictures_by_weekday$predictor_pa_volume), error = FALSE)
```

### The effects of physical activity intensity on sleep by weekday

We estimated how physical activity intensity affects sleep across weekday.
We present the results in Table \@ref(tab:sleep-outcomes-by-weekday) and Figure \@ref(fig:sleep-by-intensity-fig-by-weekday).

```{r sleep-by-intensity-fig-by-weekday, fig.cap = "Sleep metrics on Physical activity intensity moderated by weekday"}
knitr::include_graphics(here::here(purdy_pictures_by_weekday$predictor_pa_intensity), error = FALSE)
```

We estimated the effect of sleep duration on physical activity by weekday.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-weekday) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-weekday).

```{r pa-outcomes-by-weekday}
papaja::apa_table(
  model_tables_by_weekday$physical_activity$data,
  caption = model_tables_by_weekday$physical_activity$caption,
  note = model_tables_by_weekday$physical_activity$note,
  col_spanners = model_tables_by_weekday$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig-by-weekday, fig.cap = "Physical activity by sleep duration moderated by weekday"}
knitr::include_graphics(here::here(purdy_pictures_by_weekday$predictor_sleep_duration_lag), error = FALSE)
```

We estimated the effect of sleep efficiency on physical activity by weekday.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-weekday) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-weekday).

```{r PA-by-sleep-efficiency-fig-by-weekday, fig.cap = "Physical activity by sleep efficiency moderated by weekday"}
knitr::include_graphics(here::here(purdy_pictures_by_weekday$predictor_sleep_efficiency_lag), error = FALSE)
```

We estimated the effect of sleep onset on physical activity by weekday.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-weekday) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-weekday).

```{r PA-by-sleep-onset-fig-by-weekday, fig.cap = "Physical activity by sleep onset moderated by weekday"}
knitr::include_graphics(here::here(purdy_pictures_by_weekday$predictor_sleep_onset_lag), error = FALSE)
```

We estimated the effect of sleep regularity on physical activity by weekday.
Results are presented in Table \@ref(tab:pa-outcomes-by-weekday) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-weekday).

```{r PA-by-sleep-regularity-fig-by-weekday, fig.cap = "Physical activity by sleep regularity moderated by weekday"}
knitr::include_graphics(here::here(purdy_pictures_by_weekday$predictor_sleep_regularity_lag), error = FALSE)
```
\clearpage

## season

```{r}
tar_load(model_tables_by_season)
tar_load(purdy_pictures_by_season)
```

### The effects of physical activity volume on sleep by season

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
We estimated the effect of physical activity volume on sleep by season, and the results are presented in Table \@ref(tab:sleep-outcomes-by-season) and Figure \@ref(fig:sleep-by-volume-fig-by-season)

```{r sleep-outcomes-by-season}
papaja::apa_table(
  model_tables_by_season$sleep$data,
  caption = model_tables_by_season$sleep$caption,
  note = model_tables_by_season$sleep$note,
  col_spanners = model_tables_by_season$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig-by-season, fig.cap = "Sleep metrics on Physical activity volume by season"}
knitr::include_graphics(here::here(purdy_pictures_by_season$predictor_pa_volume), error = FALSE)
```

### The effects of physical activity intensity on sleep by season

We estimated how physical activity intensity affects sleep across season.
We present the results in Table \@ref(tab:sleep-outcomes-by-season) and Figure \@ref(fig:sleep-by-intensity-fig-by-season).

```{r sleep-by-intensity-fig-by-season, fig.cap = "Sleep metrics on Physical activity intensity moderated by season"}
knitr::include_graphics(here::here(purdy_pictures_by_season$predictor_pa_intensity), error = FALSE)
```

We estimated the effect of sleep duration on physical activity by season.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-season) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-season).

```{r pa-outcomes-by-season}
papaja::apa_table(
  model_tables_by_season$physical_activity$data,
  caption = model_tables_by_season$physical_activity$caption,
  note = model_tables_by_season$physical_activity$note,
  col_spanners = model_tables_by_season$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig-by-season, fig.cap = "Physical activity by sleep duration moderated by season"}
knitr::include_graphics(here::here(purdy_pictures_by_season$predictor_sleep_duration_lag), error = FALSE)
```

We estimated the effect of sleep efficiency on physical activity by season.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-season) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-season).

```{r PA-by-sleep-efficiency-fig-by-season, fig.cap = "Physical activity by sleep efficiency moderated by season"}
knitr::include_graphics(here::here(purdy_pictures_by_season$predictor_sleep_efficiency_lag), error = FALSE)
```

We estimated the effect of sleep onset on physical activity by season.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-season) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-season).

```{r PA-by-sleep-onset-fig-by-season, fig.cap = "Physical activity by sleep onset moderated by season"}
knitr::include_graphics(here::here(purdy_pictures_by_season$predictor_sleep_onset_lag), error = FALSE)
```

We estimated the effect of sleep regularity on physical activity by season.
Results are presented in Table \@ref(tab:pa-outcomes-by-season) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-season).

```{r PA-by-sleep-regularity-fig-by-season, fig.cap = "Physical activity by sleep regularity moderated by season"}
knitr::include_graphics(here::here(purdy_pictures_by_season$predictor_sleep_regularity_lag), error = FALSE)
```
\clearpage

## region

```{r}
tar_load(model_tables_by_region)
tar_load(purdy_pictures_by_region)
```

### The effects of physical activity volume on sleep by region

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
We estimated the effect of physical activity volume on sleep by region, and the results are presented in Table \@ref(tab:sleep-outcomes-by-region) and Figure \@ref(fig:sleep-by-volume-fig-by-region)

```{r sleep-outcomes-by-region}
papaja::apa_table(
  model_tables_by_region$sleep$data,
  caption = model_tables_by_region$sleep$caption,
  note = model_tables_by_region$sleep$note,
  col_spanners = model_tables_by_region$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig-by-region, fig.cap = "Sleep metrics on Physical activity volume by region"}
knitr::include_graphics(here::here(purdy_pictures_by_region$predictor_pa_volume), error = FALSE)
```

### The effects of physical activity intensity on sleep by region

We estimated how physical activity intensity affects sleep across region.
We present the results in Table \@ref(tab:sleep-outcomes-by-region) and Figure \@ref(fig:sleep-by-intensity-fig-by-region).

```{r sleep-by-intensity-fig-by-region, fig.cap = "Sleep metrics on Physical activity intensity moderated by region"}
knitr::include_graphics(here::here(purdy_pictures_by_region$predictor_pa_intensity), error = FALSE)
```

We estimated the effect of sleep duration on physical activity by region.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-region) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-region).

```{r pa-outcomes-by-region}
papaja::apa_table(
  model_tables_by_region$physical_activity$data,
  caption = model_tables_by_region$physical_activity$caption,
  note = model_tables_by_region$physical_activity$note,
  col_spanners = model_tables_by_region$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig-by-region, fig.cap = "Physical activity by sleep duration moderated by region"}
knitr::include_graphics(here::here(purdy_pictures_by_region$predictor_sleep_duration_lag), error = FALSE)
```

We estimated the effect of sleep efficiency on physical activity by region.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-region) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-region).

```{r PA-by-sleep-efficiency-fig-by-region, fig.cap = "Physical activity by sleep efficiency moderated by region"}
knitr::include_graphics(here::here(purdy_pictures_by_region$predictor_sleep_efficiency_lag), error = FALSE)
```

We estimated the effect of sleep onset on physical activity by region.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-region) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-region).

```{r PA-by-sleep-onset-fig-by-region, fig.cap = "Physical activity by sleep onset moderated by region"}
knitr::include_graphics(here::here(purdy_pictures_by_region$predictor_sleep_onset_lag), error = FALSE)
```

We estimated the effect of sleep regularity on physical activity by region.
Results are presented in Table \@ref(tab:pa-outcomes-by-region) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-region).

```{r PA-by-sleep-regularity-fig-by-region, fig.cap = "Physical activity by sleep regularity moderated by region"}
knitr::include_graphics(here::here(purdy_pictures_by_region$predictor_sleep_regularity_lag), error = FALSE)
```
\clearpage

## daylight hours

```{r}
tar_load(model_tables_by_daylight)
tar_load(purdy_pictures_by_daylight)
```

### The effects of physical activity volume on sleep by daylight hours

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
We estimated the effect of physical activity volume on sleep by daylight hours, and the results are presented in Table \@ref(tab:sleep-outcomes-by-daylight-hours) and Figure \@ref(fig:sleep-by-volume-fig-by-daylight-hours)

```{r sleep-outcomes-by-daylight-hours}
papaja::apa_table(
  model_tables_by_daylight$sleep$data,
  caption = model_tables_by_daylight$sleep$caption,
  note = model_tables_by_daylight$sleep$note,
  col_spanners = model_tables_by_daylight$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig-by-daylight-hours, fig.cap = "Sleep metrics on Physical activity volume by daylight hours"}
knitr::include_graphics(here::here(purdy_pictures_by_daylight$predictor_pa_volume), error = FALSE)
```

### The effects of physical activity intensity on sleep by daylight hours

We estimated how physical activity intensity affects sleep across daylight hours.
We present the results in Table \@ref(tab:sleep-outcomes-by-daylight-hours) and Figure \@ref(fig:sleep-by-intensity-fig-by-daylight-hours).

```{r sleep-by-intensity-fig-by-daylight-hours, fig.cap = "Sleep metrics on Physical activity intensity moderated by daylight hours"}
knitr::include_graphics(here::here(purdy_pictures_by_daylight$predictor_pa_intensity), error = FALSE)
```

We estimated the effect of sleep duration on physical activity by daylight hours.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-daylight-hours) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-daylight-hours).

```{r pa-outcomes-by-daylight-hours}
papaja::apa_table(
  model_tables_by_daylight$physical_activity$data,
  caption = model_tables_by_daylight$physical_activity$caption,
  note = model_tables_by_daylight$physical_activity$note,
  col_spanners = model_tables_by_daylight$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig-by-daylight-hours, fig.cap = "Physical activity by sleep duration moderated by daylight hours"}
knitr::include_graphics(here::here(purdy_pictures_by_daylight$predictor_sleep_duration_lag), error = FALSE)
```

We estimated the effect of sleep efficiency on physical activity by daylight hours.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-daylight-hours) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-daylight-hours).

```{r PA-by-sleep-efficiency-fig-by-daylight-hours, fig.cap = "Physical activity by sleep efficiency moderated by daylight hours"}
knitr::include_graphics(here::here(purdy_pictures_by_daylight$predictor_sleep_efficiency_lag), error = FALSE)
```

We estimated the effect of sleep onset on physical activity by daylight hours.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-daylight-hours) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-daylight-hours).

```{r PA-by-sleep-onset-fig-by-daylight-hours, fig.cap = "Physical activity by sleep onset moderated by daylight hours"}
knitr::include_graphics(here::here(purdy_pictures_by_daylight$predictor_sleep_onset_lag), error = FALSE)
```

We estimated the effect of sleep regularity on physical activity by daylight hours.
Results are presented in Table \@ref(tab:pa-outcomes-by-daylight-hours) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-daylight-hours).

```{r PA-by-sleep-regularity-fig-by-daylight-hours, fig.cap = "Physical activity by sleep regularity moderated by daylight hours"}
knitr::include_graphics(here::here(purdy_pictures_by_daylight$predictor_sleep_regularity_lag), error = FALSE)
```
\clearpage

## wear location

```{r}
tar_load(model_tables_by_wear_location)
tar_load(purdy_pictures_by_wear_location)
```

### The effects of physical activity volume on sleep by wear location

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
We estimated the effect of physical activity volume on sleep by wear location, and the results are presented in Table \@ref(tab:sleep-outcomes-by-acc-wear-loc) and Figure \@ref(fig:sleep-by-volume-fig-by-acc-wear-loc)

```{r sleep-outcomes-by-acc-wear-loc}
papaja::apa_table(
  model_tables_by_wear_location$sleep$data,
  caption = model_tables_by_wear_location$sleep$caption,
  note = model_tables_by_wear_location$sleep$note,
  col_spanners = model_tables_by_wear_location$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig-by-acc-wear-loc, fig.cap = "Sleep metrics on Physical activity volume by wear location"}
knitr::include_graphics(here::here(purdy_pictures_by_wear_location$predictor_pa_volume), error = FALSE)
```

### The effects of physical activity intensity on sleep by wear location

We estimated how physical activity intensity affects sleep across wear location.
We present the results in Table \@ref(tab:sleep-outcomes-by-acc-wear-loc) and Figure \@ref(fig:sleep-by-intensity-fig-by-acc-wear-loc).

```{r sleep-by-intensity-fig-by-acc-wear-loc, fig.cap = "Sleep metrics on Physical activity intensity moderated by wear location"}
knitr::include_graphics(here::here(purdy_pictures_by_wear_location$predictor_pa_intensity), error = FALSE)
```

We estimated the effect of sleep duration on physical activity by wear location.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-acc-wear-loc) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-acc-wear-loc).

```{r pa-outcomes-by-acc-wear-loc}
papaja::apa_table(
  model_tables_by_wear_location$physical_activity$data,
  caption = model_tables_by_wear_location$physical_activity$caption,
  note = model_tables_by_wear_location$physical_activity$note,
  col_spanners = model_tables_by_wear_location$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig-by-acc-wear-loc, fig.cap = "Physical activity by sleep duration moderated by wear location"}
knitr::include_graphics(here::here(purdy_pictures_by_wear_location$predictor_sleep_duration_lag), error = FALSE)
```

We estimated the effect of sleep efficiency on physical activity by wear location.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-acc-wear-loc) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-acc-wear-loc).

```{r PA-by-sleep-efficiency-fig-by-acc-wear-loc, fig.cap = "Physical activity by sleep efficiency moderated by wear location"}
knitr::include_graphics(here::here(purdy_pictures_by_wear_location$predictor_sleep_efficiency_lag), error = FALSE)
```

We estimated the effect of sleep onset on physical activity by wear location.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-acc-wear-loc) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-acc-wear-loc).

```{r PA-by-sleep-onset-fig-by-acc-wear-loc, fig.cap = "Physical activity by sleep onset moderated by wear location"}
knitr::include_graphics(here::here(purdy_pictures_by_wear_location$predictor_sleep_onset_lag), error = FALSE)
```

We estimated the effect of sleep regularity on physical activity by wear location.
Results are presented in Table \@ref(tab:pa-outcomes-by-acc-wear-loc) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-acc-wear-loc).

```{r PA-by-sleep-regularity-fig-by-acc-wear-loc, fig.cap = "Physical activity by sleep regularity moderated by wear location"}
knitr::include_graphics(here::here(purdy_pictures_by_wear_location$predictor_sleep_regularity_lag), error = FALSE)
```
\clearpage

## most active hour

```{r}
tar_load(model_tables_by_pa_mostactivehr)
tar_load(purdy_pictures_by_pa_mostactivehr)
```

### The effects of physical activity volume on sleep by most active hour

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
We estimated the effect of physical activity volume on sleep by most active hour, and the results are presented in Table \@ref(tab:sleep-outcomes-by-pa-mostactivehr) and Figure \@ref(fig:sleep-by-volume-fig-by-pa-mostactivehr)

```{r sleep-outcomes-by-pa-mostactivehr}
papaja::apa_table(
  model_tables_by_pa_mostactivehr$sleep$data,
  caption = model_tables_by_pa_mostactivehr$sleep$caption,
  note = model_tables_by_pa_mostactivehr$sleep$note,
  col_spanners = model_tables_by_pa_mostactivehr$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig-by-pa-mostactivehr, fig.cap = "Sleep metrics on Physical activity volume by most active hour"}
knitr::include_graphics(here::here(purdy_pictures_by_pa_mostactivehr$predictor_pa_volume), error = FALSE)
```

### The effects of physical activity intensity on sleep by most active hour

We estimated how physical activity intensity affects sleep across most active hour.
We present the results in Table \@ref(tab:sleep-outcomes-by-pa-mostactivehr) and Figure \@ref(fig:sleep-by-intensity-fig-by-pa-mostactivehr).

```{r sleep-by-intensity-fig-by-pa-mostactivehr, fig.cap = "Sleep metrics on Physical activity intensity moderated by most active hour"}
knitr::include_graphics(here::here(purdy_pictures_by_pa_mostactivehr$predictor_pa_intensity), error = FALSE)
```

We estimated the effect of sleep duration on physical activity by most active hour.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-pa-mostactivehr) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-pa-mostactivehr).

```{r pa-outcomes-by-pa-mostactivehr}
papaja::apa_table(
  model_tables_by_pa_mostactivehr$physical_activity$data,
  caption = model_tables_by_pa_mostactivehr$physical_activity$caption,
  note = model_tables_by_pa_mostactivehr$physical_activity$note,
  col_spanners = model_tables_by_pa_mostactivehr$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig-by-pa-mostactivehr, fig.cap = "Physical activity by sleep duration moderated by most active hour"}
knitr::include_graphics(here::here(purdy_pictures_by_pa_mostactivehr$predictor_sleep_duration_lag), error = FALSE)
```

We estimated the effect of sleep efficiency on physical activity by most active hour.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-pa-mostactivehr) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-pa-mostactivehr).

```{r PA-by-sleep-efficiency-fig-by-pa-mostactivehr, fig.cap = "Physical activity by sleep efficiency moderated by most active hour"}
knitr::include_graphics(here::here(purdy_pictures_by_pa_mostactivehr$predictor_sleep_efficiency_lag), error = FALSE)
```

We estimated the effect of sleep onset on physical activity by most active hour.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-pa-mostactivehr) and Figure \@ref(fig:PA-by-sleep-onset-fig-by-pa-mostactivehr).

```{r PA-by-sleep-onset-fig-by-pa-mostactivehr, fig.cap = "Physical activity by sleep onset moderated by most active hour"}
knitr::include_graphics(here::here(purdy_pictures_by_pa_mostactivehr$predictor_sleep_onset_lag), error = FALSE)
```

We estimated the effect of sleep regularity on physical activity by most active hour.
Results are presented in Table \@ref(tab:pa-outcomes-by-pa-mostactivehr) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-pa-mostactivehr).

>>>>

In the following section we present models for a range of moderators which were pre-defined in our protocol.
